Routines and Regret: An Examination of Behavioral Norms and Emotional Responses

### 2024-02-15 paper/paper.qmd
modify

dataset_selected_exp1 <- data %>% select(Sc1_regret, sc1_socnorms1, sc1_socnorms2, sc1_combinednorms)
kable(head(dataset_selected_exp1))
```

>>>>

dataset_selected_exp1 <- data %>% select(Sc1_regret, sc1_socnorms1, sc1_socnorms2, sc1_combinednorms)
kable(head(dataset_selected_exp1))

# Save the cleaned data
write_csv(
  x = data,
  file = here::here("data/analysis_data/exp1-labeled-data.csv")
)
```
```
